\documentclass[11pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{xcolor}
\usepackage{booktabs}
\usepackage{enumitem}
\usepackage{fancyhdr}
\usepackage{geometry}

% Page layout
\geometry{margin=1in}
\pagestyle{fancy}
\fancyhf{}
\fancyhead[L]{Trustworthy Machine Learning}
\fancyhead[R]{Lesson 6}
\fancyfoot[C]{\thepage}

% Custom commands
\newcommand{\concept}[1]{\textbf{#1}}
\newcommand{\note}[1]{\textcolor{blue}{\textit{#1}}}

\title{Trustworthy Machine Learning\\
\large Lesson 6 Recap}
\author{Your Name}
\date{\today}

\begin{document}

\maketitle
\tableofcontents
\newpage

\section{Introduction}
This document contains a recap of Lesson 6 of the Trustworthy Machine Learning course. It includes a summary of the key concepts covered, important definitions, and answers to questions that arose during the class.

\section{Summary}
% Brief overview of what was covered in the lesson
In this sixth lesson, we covered...

\section{Key Concepts}
\subsection{Concept 1}
% Detailed explanation of the first key concept

\subsection{Concept 2}
% Detailed explanation of the second key concept

\section{Important Definitions}
\begin{itemize}
    \item \concept{Term 1}: Definition of the first term.
    \item \concept{Term 2}: Definition of the second term.
\end{itemize}

\section{Examples and Applications}
% Examples that illustrate the concepts

\section{Questions and Clarifications}
% Questions that came up during class and their answers
\begin{enumerate}
    \item \textbf{Question:} First question that was asked.
    
    \textbf{Answer:} The answer to the first question.
    
    \item \textbf{Question:} Second question that was asked.
    
    \textbf{Answer:} The answer to the second question.
\end{enumerate}

\section{Additional Resources}
% Links to papers, websites, or other resources that might be helpful
\begin{itemize}
    \item Resource 1: Brief description
    \item Resource 2: Brief description
\end{itemize}

\section{Summary of Key Takeaways}
% The most important points to remember from this lesson

\end{document}
